\documentclass[12pt]{article}

\usepackage{paper}

%commands
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\theequation}{\arabic{equation}}

\date{}

\begin{document}
{\Large\noindent
[Overview\footnote{
Written by Daichi Takeda (takedai.gauge@gmail.com)
}]
\hfill{\normalsize last updated: \today}
\\[2mm]
%title
\textbf{Nuts and Bolts for Creating Space\cite{Czech:2014ppa}
}
}

\noindent
\hfill
\textbf{Bartlomiej Czech, Lampros Lamprou}%author

\renewcommand{\thefootnote}{\arabic{footnote})}
\setcounter{footnote}{0}
\vspace{12pt}
%%body

They introduced the method to reconstruct a time slice surface of $\mathrm{AdS}_3$ from the differential entropy of 
$\mathrm{CFT}_2$ \cite{Balasubramanian:2013lsa} 
(see \href{https://albertmcc.github.io/web/overview_papers/Hole_ographic_spacetime.pdf}{\color{blue}my overview}).
Specifically they found the method to detect the bulk points and to measure the distances between two points 
on the time slice.


\subsubsection*{The detection of points}
Let $\alpha(\theta)$ be a boundary function introduced in \cite{Balasubramanian:2013lsa}, which is also seen in 
\href{https://albertmcc.github.io/web/overview_papers/Hole_ographic_spacetime.pdf}.\footnote{
The notation adopted here is checked in  my overview.}
Any bulk closed curve $R = R(\phi)$ corresponds to a certain boundary function $\alpha(\theta)$.
In the limit of the bulk curve shrinking, the curve becomes a point.

They used this shrinking limit to find the way to detect bulk points from the boundary.
First, Gauss-Bonnet theorem states that the following relation holds in negatively curved spaces:
\begin{align}
	\oint_{\partial A}\d\tau \sqrt{h}K = 2\pi - \int_A \d A\,R\ge 2\pi.\label{eq:Gauss}
\end{align}
Here $\partial A$ means the closed curve $R = R(\phi)$, $A$ is the area enclosed by the curve, $\d\tau\sqrt{h}$ is the line
 element along the curve, $K$ is the extrinsic curvature, and $\d A$ is the areal element.
In the shrinking limit, we obtain
\begin{align}
	\lim_{A\to \mathrm{point}} ~\oint_{\partial A}\d\tau \sqrt{h}K = 2\pi.
\end{align}
In addition, the integrand of l.h.s.\ in \eqref{eq:Gauss} can be expressed by $\alpha(\theta)$ as
\begin{align}
	\d\tau \sqrt{h} K = \frac{\d\theta\sqrt{1-\alpha'(\theta)^2}}{\sin\alpha(\theta)}.
\end{align}

From these facts, the boundary function $\alpha(\theta)$ corresponds to a certain bulk point 
if and only if it extremizes the functional
\begin{align}
	I[\alpha] = \int_0^{2\pi}\d\theta \frac{\sqrt{1-\alpha'(\theta)^2}}{\sin\alpha(\theta)},\label{eq:action}
\end{align}
of which the Euler-Lagrange equation is a second order differential equation.
Therefore, $\alpha(\theta)$ has two constants, which we regard as a bulk point on the time slice.
Noting the relation
\begin{align}
	\frac{1}{\sin^2\alpha} = -\frac{2G}{L}\frac{\d^2S(\alpha)}{\d\alpha^2},
\end{align}
the action \eqref{eq:action} can be rewritten as 
\begin{align}
	I[\alpha] = \int_0^{2\pi}\d\theta\,\sqrt{-\l.\frac{\d^2S(\alpha)}{\d\alpha^2}\r|_{\alpha = \alpha(\theta)}(1-\alpha'(\theta)^2)}~~.\label{eq:aaction}
\end{align}
They conjectured that this action also holds for other cases having the rotational symmetry.
In other words, the collection of functions $\alpha(\theta)$ extremizing \eqref{eq:aaction} is the copy of the bulk points.
The elements of the collection are called ``point function" here.\footnote{There is no specific terminology yet.}
A counterexample is discussed in \cite{Burda:2018rpb} 
(see \href{https://albertmcc.github.io/web/reviews/holographic_bubble.pdf}{\color{blue}my overview}).

\subsubsection*{The measurement of distances}

Next, let us see the holographic distances introduced by them, which is defined in the set of point functions $\mathcal P$.
Now the differential entropy $E[\alpha]$ is used to define the distance.

Let us define $\gamma_{AB}(\theta) := \min\{\alpha_A(\theta),\alpha_B(\theta)\}$ for $\alpha_A,\alpha_B\in\mathcal P$ 
($\gamma$ is defined as a point-wise minimum among $\alpha_A$ and $\alpha_B$).
The functional $d(A,B)$ defined as follows is the holographic distance between 
$A$ and $B$ measured in the units of $4G$:
\begin{align}
	d(A,B) := \frac{1}{2}E[\gamma].\label{eq:dist}
\end{align}
It is shown that this functional satisfies the axioms of a distance function.\footnote{
Note that this is the distance defined on a time slice, so the distance is always positive.}

In the remaining, we see why $d(A,B)$ can be regarded as the distance on the time slice.
Let us consider that a boundary function $\alpha(\theta)$ has a point $\theta_k$ at which $\alpha'(\theta)$ jumps.
From the corollary shown in \cite{Balasubramanian:2013lsa}, we have
\begin{align}
	E[\alpha] &= \frac{1}{2}\int_{0}^{\theta_k-0}\d\theta\,\l.\frac{\d S(\alpha)}{\d \alpha}\r|_{\alpha = \alpha(\theta)} + \frac{1}{2}\int_{\theta_k+0}^{2\pi}\d\theta\,\l.\frac{\d S(\alpha)}{\d \alpha}\r|_{\alpha = \alpha(\theta)}\nonumber\\[2mm]
	&= \frac{(\mbox{left length}) + (\mbox{right length}) + (\mbox{geodesic length in } \phi(\theta_k-0)\leq \phi\leq \phi(\theta_k+0))}{4G}.
\end{align}
This means that the bulk curve $(R,\phi) = (R(\theta),\phi(\theta))$ corresponding to $\alpha(\theta)$ has a jump at $\theta_k$,
and the following holds with the curve compensated by the geodesic:
\begin{align}
	E[\alpha] = \frac{\mbox{length}}{4G}.
\end{align}
The relation is introduced in \cite{Balasubramanian:2013lsa}.
(see \href{https://albertmcc.github.io/web/overview_papers/Hole_ographic_spacetime.pdf}).

Let us consider $\gamma(\theta) = \min\{\alpha(\theta),\beta(\theta)\}$ with $\alpha$ and $\beta$ smooth.
Generally, $\gamma$ has points at which $\gamma'(\theta)$ jumps, and these points correspond to the points $\gamma$
 changes the value from $\alpha$ to $\beta$ or vice versa.
Therefore, for each $\theta_0$ at which $\gamma$ jumps, there must exist a geodesic which smoothly connects 
$(R_\alpha(\theta_0),\phi_\alpha(\theta_0))$ and $(R_\beta(\theta_0),\phi_\beta(\theta_0))$, where 
$(R_\alpha(\theta),\phi_\alpha(\theta))$ is a curve corresponding to $\alpha$ and $(R_\beta(\theta),\phi_\beta(\theta))$ to 
$\beta$.
This means that there is a convex curve which covers $(R_\alpha(\theta),\phi_\alpha(\theta))$ and 
$(R_\beta(\theta),\phi_\beta(\theta))$ (see Figure 6 in \cite{Czech:2014ppa}).
In the shrinking limit of $(R_\alpha(\theta),\phi_\alpha(\theta))\to A$ and $(R_\beta(\theta),\phi_\beta(\theta))\to B$, 
the convex curve becomes the identical two geodesic going from $A$ to $B$, by which we can verify \eqref{eq:dist}.

The extension to conical defect $\mathrm{AdS}_3$ and BTZ are also discussed in the paper.












%%
\bibliographystyle{jhep} 
\bibliography{reference.bib}
\end{document}
